A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
new related text

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit a
natural hierarchical decomposition of the underlying POMDP into
subproblems where decision-theoretic planning is reasonably
fast. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief space ---essentially the idea that
it does not matter what the value of the variable you are trying to
observe is--- to exponentially shrink the state space. Although we
have been actively exploring the \citeauthor{doshi08:pref_elic}
approach, those exploitable structures are not present in problems we
have considered so far due to the task planning requirement. 
%%
%%
Finally,
our approach is in a similar vein to the more classical {\em
dual-mode} control~\cite{cassandra96actingunder}, however in our case
entropy reduction is targeted by planning in an abstract process which
is informed by one execution trace ---computed by a {\em classical}
planner--- and the underlying belief-state.

>>>>

%%  ---essentially the idea that
%% it does not matter what the value of the variable you are trying to
%% observe is---

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit an
explicitly modelled hierarchical decomposition of the underlying
POMDP. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief space to exponentially shrink the
state space. Although we have been actively exploring
the \citeauthor{doshi08:pref_elic} approach, those exploitable
symmetries are not present in problems we have considered so far due
to the task planning requirement.
%%
Finally, our approach is in a similar vein to {\em dual-mode}
control~\cite{cassandra96actingunder}, in our case we use a {\em
classical} planner to provide guidance for reducing entropy.

%% entropy reduction is targeted by planning in an abstract process which
%% is informed by one execution trace ---computed by a {\em classical}
%% planner--- and the underlying belief-state.
